---
title: "第二章"
author: "zfwang"
date: "2017年3月9日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	fig.height = 8,
	fig.width = 8, 
	message = FALSE
)
```

## Table of Contents

2. Quickly Exploring Data
    - 2.1. Creating a **Scatter Plot** 7
    - 2.2. Creating a **Line Graph** 9
    - 2.3. Creating a **Bar Graph** 11
    - 2.4. Creating a **Histogram** 13
    - 2.5. Creating a **Box Plot** 15
    - 2.6. Plotting a **Function Curve** 17


-----

## Requalied Packages

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(gcookbook)
library(plyr)
library(dplyr)
library(MASS)
```

    
## 2. Quickly Exploring Data

### 2.1 Scatter Plot

#### (1)plot()

```{r}
plot(mtcars$wt, mtcars$mpg, main = "Scatter plot with base graphics")
```
















#### (2)qplot()

```{r, message = FALSE}
q1 <- qplot(mtcars$wt, mtcars$mpg) + 
    ggtitle("Scatter plot with qplot() from ggplot2")
q2 <- qplot(wt, mpg, data = mtcars) + 
    ggtitle("Scatter plot with qplot() from ggplot2")
library(gridExtra)
grid.arrange(q1, q2, ncol = 2)
```

#### (3)ggplot()

```{r}
ggplot(data = mtcars, aes(x = wt, y = mpg)) + 
    geom_point() +
    ggtitle("Scatter plot with ggplot() from ggplot2")
```


### 2.2 Line Graph

#### (1)plot(), pooint(), line()

```{r}
plot(pressure$temperature, pressure$pressure, type = "l", main = "line graph with base graphics")
```

```{r}
plot(pressure$temperature, pressure$pressure, type = "l", main = "line graph with base graphics")
points(pressure$temperature, pressure$pressure)
```

```{r}
plot(pressure$temperature, pressure$pressure, type = "l", main = "line and point graph with base graphics")
points(pressure$temperature, pressure$pressure)
lines(pressure$temperature, pressure$pressure/2, col = "red")
points(pressure$temperature, pressure$pressure/2, col = "red")
```

#### (2)qplot()

```{r}
q3 <- qplot(temperature, pressure, data = pressure, geom = "line") +
    ggtitle("line graph with qplot() from ggplot2")
q4 <- qplot(temperature, pressure, data = pressure, geom = c("line", "point")) + 
    ggtitle("line and point graph with qplot() from ggplot2")
grid.arrange(q3, q4, ncol = 2)
```

#### (3)ggplot()

```{r}
ggplot(data = pressure, aes(x = temperature, y = pressure)) + 
    geom_line() + 
    ggtitle("line graph with ggplot() from ggplot2")
ggplot(data = pressure, aes(x = temperature, y = pressure)) + 
    geom_line() + 
    geom_point() + 
    ggtitle("line graph with ggplot() from ggplot2")
```

### 2.3 Bar Graph

#### (1)barplot()

data:

```{r}
BOD
```

```{r}
barplot(BOD$demand)
barplot(BOD$demand, names.arg = BOD$Time)
```

```{r}
barplot(mtcars$cyl)
table(mtcars$cyl)
barplot(table(mtcars$cyl))
```

#### (2)ggplot()

```{r}
ggplot(data = BOD, aes(x = Time, y = demand)) + 
    geom_bar(stat = "identity")
# Convert the x variable to a factor, so that it is treated as discrete
ggplot(data = BOD, aes(x = factor(Time), y = demand)) + 
    geom_bar(stat = "identity")
```

```{r}
qplot(cyl, data = mtcars)
ggplot(mtcars, aes(x = cyl)) + geom_bar()
qplot(factor(cyl), data = mtcars)
ggplot(mtcars, aes(x = factor(cyl))) + geom_bar()
```

### 2.4 Histogram

#### view the distribution of one-dimensional data

```{r}
hist(mtcars$mpg)
hist(mtcars$mpg, breaks = 10)
```

```{r}
qplot(mpg, data = mtcars)
qplot(mpg, data = mtcars, binwidth = 4)
ggplot(data = mtcars, aes(mpg)) + 
    geom_histogram(binwidth = 4)
```

### 2.5 Box Plot

#### comparing distributions

```{r}
head(ToothGrowth)
plot(ToothGrowth$supp, ToothGrowth$len)
```

```{r}
boxplot(len ~ supp, data = ToothGrowth)
```

```{r}
boxplot(len ~ supp + dose, data = ToothGrowth)
```

```{r}
qplot(x = supp, y = len, data = ToothGrowth, geom = "boxplot")
ggplot(data = ToothGrowth, aes(x = supp, y = len)) +
    geom_boxplot()

qplot(x = interaction(supp, dose), y = len, 
      data = ToothGrowth, 
      geom = "boxplot")
ggplot(data = ToothGrowth, aes(x = interaction(supp, dose), y = len)) + 
    geom_boxplot()
```

### 2.6 Function Curve

```{r}
curve(x^3 + 5*x, from = -4, to = 4)
```

```{r}
myfun <- function(xvar) {
    1/(1 + exp(-xvar + 10))
}
curve(myfun(x), from = 0, to = 20)
```


```{r}
curve(myfun(x), from = 0, to = 20)
curve(1-myfun(x), add = TRUE, col = "red")
```

```{r}
ggplot(data = data.frame(x = c(0, 20)), aes(x = x)) + 
    stat_function(fun = myfun, geom = "line")
```
