---
title: "lattice"
author: "wangzhefeng"
date: "November 3, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# lattice

```{r, eval=F}
graph_function(formula, data = dataset, options)
```

## Base charts

* scatter and scatter matrix chart
    - xyplot()
    - splom()
* bar chart
    - barchart()
* histogram and density chart
    - histogram()
    - densityplot()
* dot chart
    - dotplot()
* daizhuang chart
    - stripplot()
* Q-Q chart
    - qqmath()
    - qq()
* box chart
    - bwplot()
* three dim chart
    - levelplot()
    - contourplot()
    - cloud()
    - wireframe()



## package install and load 

```{r, message=F}
if(!require(lattice)) install.packages('lattice')
names(trellis.par.get())
```

# 1. scatter plot 

* Function
    - xyplot()

```{r}
data = data.frame(x = seq(0, 14),
                  y = seq(1:15),
                  z = rep(c('a', 'b', 'c'), times = 5))
xyplot(y ~ x, data = data)
show.settings()
```

## 1.1 trellis parameter setting

```{r}
op = trellis.par.get()
trellis.par.get('axis.text')
trellis.par.set(list(axis.text = list(cex = 1.5, col = 'blue')))
xyplot(y ~ x, data = data)
trellis.par.set(op)
show.settings()
```

## 1.2 setting

```{r}
op = trellis.par.get()
xyplot(y ~ x, groups = z, data = data)
mysetting = trellis.par.get()
mysetting$superpose.symbol$col
mysetting$superpose.symbol$pch
mysetting$superpose.symbol$pch = 1:10
mysetting$superpose.symbol$col = 'black'
trellis.par.set(mysetting)
xyplot(y ~ x, groups = z, data = data)
trellis.par.set(op)
```

## 1.3 condition variable

```{r}
xyplot(y ~ x|z, data = data, layout = c(3, 1))

# panel.abline()
mypanel = function(...) {
  panel.abline(a = 1, b = 1)
  panel.xyplot(...)
}

xyplot(y ~ x|z, data = data, layout = c(3, 1), panel = mypanel)
```

## 1.4 group variable

```{r}
densityplot(~ mpg, data = mtcars, 
            lty = 1:2, col = 1:2, lwd = 2,
            groups = factor(am), 
            main = list("MPG Distribution by Tranamission Type", cex = 1.5),
            xlab = "Miles per Gallon",
            key = list(column = 2, 
                       space = "bottom",
                       title = "Transmission (0 = automatic, 1 = manual)",
                       text = list(levels(factor(mtcars$am))),
                       lines = list(lty = 1:2, col = 1:2, lwd = 2)))
```

## 1.5 position setting

```{r}
graph1 = xyplot(mpg ~ wt, data = mtcars, 
                xlab = "Weight", 
                ylab = "Miles Per Gallon")
displacement = equal.count(mtcars$disp, number = 3, overlap = 0)
graph2 = xyplot(mpg ~ wt|displacement, data = mtcars, layout = c(3, 1),
                xlab = "Weight", 
                ylab = "Miles Per Gallon")
```

### method 1:

```{r}
plot(graph1, split = c(1, 1, 2, 1))
plot(graph2, split = c(2, 1, 2, 1), newpage = FALSE)
```

### method 2:

```{r}
plot(graph1, position = c(0, 0, 0.5, 1))
plot(graph2, position = c(0.5, 0, 1, 1), newpage = FALSE)
```



# 2. bar chart


```{r, eval=F}
barchart(table, ...)
barchart(formula, data = data.frame, ...)
# panel function
panel.barchart()
```

```{r}
str(Titanic)
```

```{r}
barchart(Titanic, 
         layout = c(4, 1),         # 4 columns and 1 row
         auto.key = TRUE,          # legend output
         scales = list(x = 'free') # x axis type
         )
```



```{r}
barchart(Class ~ Freq|Sex + Age, data = as.data.frame(Titanic), 
         groups = Survived, 
         stack = TRUE, 
         layout = c(4, 1),
         auto.key = list(title = 'Survived', columns = 2), 
         scales = list(x = 'free'))
```


```{r}
mygraph = barchart(Class ~ Freq|Sex + Age, 
                   data = as.data.frame(Titanic), 
                   groups = Survived, 
                   layout = c(4, 1),
                   auto.key = list(title = 'Survived', columns = 2),
                   scales = list(x = 'free'))
plot(mygraph)
print(mygraph)
mygraph
```

```{r}
update(mygraph, 
       panel = function(...) {
         panel.grid(h = 0, v = 1)
         panel.barchart(..., border = 'transparent')
       })
```

# 3. dot chart


```{r, eval = F}
dotplot(formula, data = data.frame, groups = TRUE, horizontal = TRUE)
```


```{r}
# data
VADeaths
dotplot(x = VADeaths, 
        pch = 1:4, col = 1:4, 
        main = list("Death Rates in virginia - 1940", cex = 1.5),
        xlab = "Rate (per 1000)",
        key = list(column = 4,
                   text = list(colnames(VADeaths)),
                   point = list(pch = 1:4, col = 1:4)))
```

```{r}
dotplot(x = VADeaths, 
        groups = FALSE, 
        main = list("Death Rates in Virginia - 1940", cex = 1.5),
        xlab = "Rate (per 1000)")
```

```{r}
dotplot(x = VADeaths, 
        groups = FALSE, 
        layout = c(1, 4), 
        aspect = 0.5, 
        origin = 0, 
        type = c("p", "h"),
        main = list("Death Rates in Virginia - 1940", cex = 1.3),
        xlab = "Rate (per 1000)")
```




# Scatter and Scatter matrix chart

```{r}
xyplot(x = Sepal.Length ~ Sepal.Width | Species, data = iris)
```

```{r}
xyplot(Sepal.Length ~ Sepal.Width | cut(Petal.Width, 2), data = iris)
```

```{r}
data = mtcars[, c(1, 3:7)]
group = mtcars$cyl
splom(x = data,
      groups = group,
      pscales = 0, 
      pch = 1:3, 
      col = 1:3,
      varnames = c('Miles\nper\ngallon', 
                   'Displacement\n(cu. in.)',
                   'Gross\nhorsepower', 
                   'Rear\naxle\nratio',
                   'Weight', '1/4 mile\ntime'),
      key = list(columns = 3, 
                 title = "Number of Cylinders",
                 text = list(levels(factor(mtcars$cyl))),
                 points = list(pch = 1:3, col = 1:3))
      )
```



# Three dim 

```{r}
contourplot(volcano, cuts = 20, label = FALSE)
```

```{r}
par.set = list(axis.line = list(col = "transparent"),
               clip = list(panel = "off"))
cloud(Sepal.Length ~ Petal.Length * Petal.Width, 
      data = iris,
      cex = 0.8, 
      pch = 1:3, 
      col = c("blue", "red", "green"),
      groups = Species, 
      screen = list(z = 20, x = -70, y = 0),
      par.setting = par.set, 
      scales = list(col = "black"),
      key = list(title = "Species",
                 column = 3,
                 space = "bottom",
                 text = list(levels(iris$Species)),
                 points = list(pch = 1:3, col = c("blue", "red", "green"))))
```

```{r}
wireframe(x = volcano, 
          shade = TRUE, 
          aspect = c(61 / 87, 0.4),
          light.source = c(10, 0, 10))
```

