---
title: "ggplot2"
author: "Zhefeng Wang"
date: "August 19, 2015"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Visualizing Data**

## Discover the unexpected in your data with `ggplot2`

## **Summarise**

1. Scatterplots

   + a.Aesthetics, Facets, Geoms
   
2. Bar charts

   + b.Positions
   
3. Histograms
   
   + c.Parameters
   
4. Visualizing big data

5. Saving Graphs

## **0.Simple examples**

```
install.packages("ggplot2")
```

```{r}
library(ggplot2)
```

### (1)Data: `iris`

```{r}
data(iris)
head(iris)
```

### (2)Plots

```{r}
p1 = ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length))
p1 +
    geom_point()
```

```{r}
p2 = ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species, shape = Species))
p2 + 
    geom_point()
```

```{r}
p3 = ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species, shape = Species)) 
p3 + 
    geom_point() +
    theme_bw()
```

```{r}
p4 = ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species, shape = Species)) 
p4 + 
    geom_point() +
    theme_bw() +
    geom_smooth(method = lm, se = FALSE)
```

```{r}
p5 = ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length))
p5 +
  geom_rug(aes(color = Species), position = 'jitter') +
  stat_density2d(aes(alpha = ..level.., fill = Species), geom = "polygon") + 
  theme_bw()
```

```{r}
p6 = ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length))
p6 +
  geom_rug(aes(color = Species), position = 'jitter') +
  stat_density2d(aes(alpha = ..level.., fill = Species), geom = "polygon") +
  theme_bw() +
  facet_wrap(~ Species)
```

```{r}
p7 = ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length))
p7 +
  geom_rug(aes(color = Species), position = 'jitter') +
  stat_density2d(aes(alpha = ..level.., fill = Species), geom = "polygon") +
  theme_bw() +
  facet_grid(.~ Species)
```



# **1. qplot() (quick plots in R)**

## **1. Scatterplots** 

### Data: `mpg`

```{r}
head(mpg)
```

```{r}
qplot(displ, hwy, data = mpg)
```

### Aesthetics

```{r}
qplot(displ, hwy, data = mpg, color = class)
```

```{r}
qplot(displ, hwy, data = mpg, size = class)
```

```{r, warning=FALSE}
qplot(displ, hwy, data = mpg, shape = class)
```

```{r}
qplot(displ, hwy, data = mpg, alpha = class)
```

### Faceting

```{r}
qplot(displ, hwy, data = mpg) + 
    facet_grid(.~ cyl)
```

```{r}
qplot(displ, hwy, data = mpg) + 
    facet_grid(drv ~.)
```

```{r}
qplot(displ, hwy, data = mpg) + 
    facet_grid(drv ~ cyl)
```

```{r}
qplot(displ, hwy, data = mpg) + 
    facet_wrap(~ class)
```

```{r}
qplot(displ, hwy, data = mpg) + 
    facet_grid(~ class)
```

### Geoms

```{r}
qplot(displ, hwy, data = mpg)
```

```{r}
qplot(displ, hwy, data = mpg, geom = "point")
```

```{r}
qplot(displ, hwy, data = mpg, geom = "smooth")
```

```{r}
qplot(displ, hwy, data = mpg, geom = c("point", "smooth"))
```

```{r}
qplot(displ, hwy, data = mpg) + 
    geom_smooth()
```

```{r}
qplot(class, hwy, data = mpg)
```

```{r}
qplot(class, hwy, data = mpg, geom = "boxplot")
```

```{r}
qplot(reorder(class, hwy), hwy, data = mpg, geom = "boxplot")
```

```{r}
qplot(reorder(class, hwy, FUN = median), hwy, data = mpg, geom = "boxplot")
```



## **2. Bar charts**

### **Default geoms for qplot**
* __Two variables → scatterplot (point)__
* __One continuous variable → histogram__
* __One categorical variable → bar chart__

```{r}
qplot(x, z, data = diamonds)
```

```{r}
qplot(x, data = diamonds)
```

```{r}
qplot(cut, data = diamonds)
```



### Fill

```{r}
qplot(cut, data = diamonds, geom = "bar", fill = cut)
```

```{r}
qplot(cut, data = diamonds, geom = "bar", color = cut)
```

### Position adjustments

```{r}
qplot(color, data = diamonds, geom = "bar", fill = cut)
```

```{r}
qplot(color, data = diamonds, geom = "bar", fill = cut, position = "stack")
```

```{r}
qplot(color, data = diamonds, geom = "bar", fill = cut, position = "dodge")
```

```{r}
qplot(color, data = diamonds, geom = "bar", fill = cut, position = "identity")
```

```{r}
qplot(color, data = diamonds, geom = "bar", fill = cut, position = "fill")
```


```{r}
qplot(cty, hwy, data = mpg)
```

```{r}
qplot(cty, hwy, data = mpg, position = "jitter")
```

```{r}
qplot(cty, hwy, data = mpg, geom = "jitter")
```

```{r}
qplot(cty, hwy, data = mpg, geom = "point", position = "jitter")
qplot(cty, hwy, data = mpg, geom = "jitter")
```


## **3. Histograms**

```{r}
qplot(displ, data = mpg)
```


```{r}
qplot(displ, data = mpg, binwidth = 1)
```

```{r}
qplot(carat, data = diamonds, binwidth = 1)
```

```{r}
qplot(carat, data = diamonds, binwidth = 0.1)
```

```{r}
qplot(carat, data = diamonds, binwidth = 0.01)
```


```{r}
zoom = coord_cartesian(xlim = c(55, 70))
```

```{r}
qplot(depth, data = diamonds, binwidth = 0.2) +
    zoom
```

```{r}
qplot(depth, data = diamonds, binwidth = 0.2, fill = cut) + 
    zoom
```

```{r}
qplot(depth, data = diamonds, binwidth = 0.2) +
    zoom + 
    facet_wrap(~ cut)
```

```{r}
qplot(depth, data = diamonds, binwidth = 0.2, geom = "freqpoly", color = cut) +
    zoom +
    facet_wrap(~ cut)
```

```{r}
qplot(depth, data = diamonds, binwidth = 0.2, geom = "freqpoly", color = cut) +
    zoom 
```

```{r}
qplot(depth, data = diamonds, geom = "density", color = cut) +
    zoom 
```

```{r}
qplot(price, data = diamonds, binwidth = 500) +
    facet_wrap(~ cut)
```

```{r}
qplot(price, data = diamonds, binwidth = 500, fill = cut)
```

```{r}
qplot(price, data = diamonds, binwidth = 500, geom = "freqpoly", color = cut)
```

```{r}
qplot(price, data = diamonds, binwidth = 500, geom = "density", color = cut)
```


## **4. Geoms for Big Data**

```{r}
qplot(carat, price, data = diamonds, color = cut)
```

```{r}
qplot(carat, price, data = diamonds, geom = "bin2d")
```

```{r}
library(hexbin)
qplot(carat, price, data = diamonds, geom = "hex")
```

```{r}
qplot(carat, price, data = diamonds, geom = "density2d")
```

```{r}
qplot(carat, price, data = diamonds, geom = c("point", "density2d"))
```

```{r}
qplot(carat, price, data = diamonds, geom = "smooth")
```

```{r}
qplot(carat, price, data = diamonds, geom = "smooth", color = cut)
```

```{r}
qplot(carat, price, data = diamonds, geom = "smooth", color = cut, se = FALSE)
```

```{r}
qplot(carat, price, data = diamonds, geom = "smooth", color = cut, se = FALSE, method = lm)
```

```{r}
qplot(carat, price, data = diamonds, geom = "smooth", group = cut)
```


### Size and transparency

```{r}
qplot(carat, price, data = diamonds, color = "blue")
```

```{r}
qplot(carat, price, data = diamonds, color = I("blue"))
```

```{r}
qplot(carat, price, data = diamonds)
```

```{r}
qplot(carat, price, data = diamonds, size = I(0.5))
```

```{r}
qplot(carat, price, data = diamonds, alpha = I(0.1))
```

```{r}
qplot(carat, price, data = diamonds, size = I(0.5), alpha = I(0.1))
```

## **5. Saving graphs**

```
getwd()
dir()
```

```
# Uses size on screen:
ggsave("my-plot.pdf")
ggsave("my-plot.png")
```

```
# Specify size in inches
ggsave("my-plot.pdf", width = 6, height = 6)
```
