---
title: "ggplot2"
author: "Zhefeng Wang"
date: "August 19, 2015"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Customizing Plots**

## Polish your plots however you please with `ggplot2`

## **Summarise**

1. Titles

2. Coordinate Systems

3. Scales

4. Themes

5. Axis labels

6. Legends



# **Data**
## **Data: texas**


```{r}
setwd("D:/My Directory/DW/Intro-to-R/Day 1/data")
texas = read.csv("texas.csv")
head(texas)
```

```{r}
sapply(texas, class)
```

```{r}
library(ggplot2)
```


```{r}
qplot(long, lat, data = texas)
```

```{r}
qplot(long, lat, data = texas, geom = "polygon", group = group)
```



## **Data: maps**

```
install.packages("maps")
```

```{r}
library(maps)
library(ggplot2)
```

```{r}
counties = map_data("county")
```

```{r}
qplot(long, lat, data = counties, geom = "polygon", group = group, fill = group)
```


```
help(package = "maps")
```

# **Manipulating plots**

```{r}
cp = qplot(carat, price, data = diamonds)
class(cp)
str(cp)
cp$coordinate
```


# **1.Title**

```{r}
tx = qplot(long, lat, data = texas, geom = "polygon", group = group, fill = bin)
tx2 = tx +ggtitle("Populayion of Texas Counties")
```

```{r}
library(gridExtra)
grid.arrange(tx, tx2, nrow = 1)
```

# **2.Coordinate systems**

## Usual Data: diamonds

```{r}
cp = qplot(carat, price, data = diamonds)
```

```{r}
cp1 = cp = cp + coord_cartesian()
```

```{r}
cp2 = cp + coord_polar()
```

```{r}
cp3 = cp + coord_flip()
```

```{r}
cp4 = cp + coord_fixed(ratio = 1/10000)
```

```{r}
cp5 = cp + coord_trans(ytrans = "log10")
```

```{r}
cp6 = cp + coord_trans(ytrans = "log10", xtrans = "log10")
```

```{r}
cp7 = cp + coord_cartesian(ylim = c(0:5000), xlim = c(0:1))
```

```{r}
library(gridExtra)
grid.arrange(cp1, cp2, cp3, cp4, cp5, cp6, cp7, nrow = 3)
```


## Map data: texas

```{r}
tx = qplot(long, lat, data = texas, geom = "polygon", group = group, fill = bin)
tx1= tx + coord_map()
```

```{r}
library(gridExtra)
grid.arrange(tx, tx1, ncol = 2)
```


## Pie charts

* **Aside: In the grammar of graphics, a pie chart is a stacked bar graph in polar coordinates.**


```{r}
d2 = subset(diamonds, color == "D")

cc = qplot(color, data = d2, fill = cut, position = "fill")

cc2 = cc + coord_polar(theta = "y")

library(gridExtra)
grid.arrange(cc, cc2, nrow = 1)
```

# **3.Scale**

> **Color Shape Size**

```{r}
hd1 <- qplot(displ, hwy, data = mpg, color = class, shape = class, size = class)
hd1
```

## Color


* **Discrete**

    + nice looking color scheme(palette)       
    + `scale_color_brewer()`    
    + `scale_fill_brewer()`   
    
    + the exact colors you list (values)    
    + `scale_color_manual()`    
    + `scale_fill_manual()`    
    
    + hues evenly spaced throughout HCL color space(h, c, l)       
    + `scale_color_hue()`    
    + `scale_fill_hue()`    


* **Discrete or Continuous**

    + greyscale values
    + `scale_color_grey()`    
    + `scale_fill_grey()`    

* **Continuous**

    + gradient between a low color and a high color(low, high)   
    + `scale_color_gradient()`    
    + `scale_fill_gradient()`    
    
    + gradient with neutral midrange and opposite colored extremes(low, mid, high, midpoint)  
    + `scale_color_gradient2()`    
    + `scale_fill_gradient2()` 
    
    + gradient that moves through range of colors(colours)      
    + `scale_color_gradientn()`    
    + `scale_fill_gradientn()`     





### Data: mpg `scale_color_gradient`

```{r}
hd2 = qplot(displ, hwy, data = mpg, color = cty)
hd2
```

```{r}
hd3 = hd2 + scale_color_gradient(low = "red", high = "yellow")
hd3
```


### Map data: texas

```{r}
tx = qplot(long, lat, data = texas, geom = "polygon", group = group, fill = bin)
tx
```

#### (1).Brewer

```{r}
library(RColorBrewer)
display.brewer.all()

tx + 
    scale_fill_brewer(palette = "Greens")

tx + 
    scale_fill_brewer(palette = "OrRd")

tx + 
    scale_fill_brewer(palette = "Spectral")

tx + 
    scale_fill_brewer(palette="OrRd")


```

#### (2).Manual

```{r}
tx + 
    scale_fill_manual(values = c("red", "orange", "yellow", "green", "blue"))
```

#### (3).Hug

```{r}
tx + 
    scale_fill_hue(h = c(150, 300), c = 150, l = 60)
```


## Size

```{r}
hd4 = qplot(displ, hwy, data = mpg, size = cyl)

hd5 = hd4 + scale_size_area()
```

```{r}
library(gridExtra)
grid.arrange(hd4, hd5, nrow = 1)
```

## Shape

```{r}
hd6 = qplot(displ, hwy, data = mpg, shape = fl)

hd7 = hd6 + scale_shape_manual(values = c(0, 15, 1, 16, 3))
```

```{r}
library(gridExtra)
grid.arrange(hd6, hd7, nrow = 2)
```



# **4.Themes**

## Help

```
?theme
```

[Theme](https://github.com/wch/ggplot2/wiki/New-theme-system)


## Sample

```{r}
tx + 
    theme_grey()
tx + 
    theme_bw()
tx + 
    theme(panel.border = element_rect(colour = "black", fill = NA))

```

## ggthemes

```{r}
library(ggthemes)
p = qplot(color, data = diamonds, fill = cut, position = "dodge")
p
```

```{r}
p + 
    theme_excel() + 
    scale_fill_excel()
p + 
    theme_economist() +
    scale_fill_economist()
p + 
    theme_few() + 
    scale_fill_few()
p + 
    theme_solarized() + 
    scale_fill_solarized()
p + 
    theme_stata() + 
    scale_fill_stata()
p + 
    theme_tufte() + 
    scale_fill_tableau()
p + 
    theme_gdocs() + 
    scale_fill_gdocs()
p + 
    theme_wsj() +
    scale_fill_wsj(palette = "black_green")
```

# **5.Axis labels**

```{r}
p = qplot(color, data = diamonds, fill = cut, position = "dodge")
```

```{r}
p1 = p + ylab("Price in Dollars ($)")
```

```{r}
p2 = p + ylab("")
```

```{r}
library(gridExtra)
grid.arrange(p, p1, p2, nrow = 3)
```

# **6.Legends**

```{r}
q = qplot(displ, hwy, data = mpg, color = cty)
```

```{r}
q + 
    theme(legend.position = "left")
q + 
    guides(color = "colorbar")
q + 
    guides(color = "legend")
q + 
    guides(color = "none")
```

```{r}
tx + 
    scale_fill_grey(name = "Legend")

tx + 
    scale_fill_grey(name = "Legend", labels = c("label 1", "label 2", "label 3","label 4", "label 5"))

tx + 
    scale_fill_discrete(name = "Legend name")
```




```{r}
tx + 
    scale_fill_brewer(palette = "Blues", name = "Population",
                      labels = c("0 - 999","1,000 - 9,999","10,000 - 99,999","100,000 - 999,999","1,000,000+")) +
    xlab("") +
    ylab("") +
    theme_bw() +
    coord_map() +
    ggtitle("Population of Texas Counties")
```



```
library(ggplot2)
library(extrafont)
loadfonts()

p + scale_fill_grey() + 
    ggtitle("Made with extrafont") + 
    theme(text = element_text(size=16, family = "Orbitron", colour = "red"))

ggsave("fonttest-orbitron.pdf")

embed_fonts("fonttest-orbitron.pdf")
```